Temporal stability in human interaction networks: sector sizes, topological prominence and time activity (Supporting Information)

### 2015-08-21 supportingInformation.tex
desinvertidas secoes de seccionamento e de pca

\title[Interaction networks stability (Supporting Information)]{Time stability in human interaction networks (Supporting Information)}% Force line breaks with \\

@@

\section{Fraction of participants in each Erd\"os Sector along the timeline}\label{si:frac}
	Here we present the fraction of participants in each Erd\"os sector with respect to each criterion defined in Section~\ref{sectioning} of the main document~\cite{tpaper}. Step sizes of 50, 100, 250, 500, 1000 and 5000 are shown bellow, first for CPP, than for  LAD list.

@@

\section{Stability in other networks: Twitter, Facebook, Participa.br}\label{si:ext}
To further verify the hypothesis that such stability is a general property of human social networks,
we analyzed networks from Twitter, Facebook and Participa.br. Selected networks are summarized in
Table~\ref{tab:E}. Their Erd\"os sector relative sizes are given in Table~\ref{tab:secE}. PCA formations are given in
Tables~\ref{tab:pcaE1F},~\ref{tab:pcaE1I},~\ref{tab:pcaE2} and~\ref{tab:pcaE3}. The friendship networks considered are undirected and unweighted, therefore all measurements of strength, in- and out- centralities, asymmetry and disequilibrium have little or no meaning, which is why F1, F2, F3, F4 and F5 are only present in Table~\ref{tab:pcaE1F}.
The most important results from this analysis are:

>>>>

\title[Interaction networks stability (Supporting Information)]{Temporal stability in human interaction networks: sector sizes, topological prominence and time activity (Supporting Information)}% Force line breaks with \\

@@

\FloatBarrier
\section{Fraction of participants in each Erd\"os Sector along the timeline}\label{si:frac}
	Here we present the fraction of participants in each Erd\"os sector with respect to each criterion defined in Section~\ref{sectioning} of the main document~\cite{tpaper}. Step sizes of 50, 100, 250, 500, 1000 and 5000 are shown below, first for CPP, then for  LAD list.

@@

\FloatBarrier
\section{Stability in other networks: Twitter, Facebook, Participa.br}\label{si:ext}
To further verify the hypothesis that such stability is a general property of human social networks,
we analyzed networks from Twitter, Facebook and Participa.br. Selected networks are summarized in
Table~\ref{tab:E}. Their Erd\"os sector relative sizes are given in Table~\ref{tab:secE}. PCA formations are given in
Tables~\ref{tab:pcaE1F},~\ref{tab:pcaE1I},~\ref{tab:pcaE2} and~\ref{tab:pcaE3}. The friendship networks considered are undirected and unweighted, therefore all measurements of strength, in- and out- centralities, asymmetry and disequilibrium have little or no meaning, which is why F1, F2, F3, F4 and F5 are only present in Table~\ref{tab:pcaE1F}.
The most important results from this analysis are:
